A New Method of Modelling Tuneable Lasers with Functional Composition

### 2019-11-13 Papers/Journal/Tuneable_Lasers.tex
Made 3d plot

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{xcolor,graphicx}
%\usepackage[subfolder,cleanup]{gnuplottex}
%\usepackage{amsthm}
%\usepackage{enumitem}
%\usepackage{wrapfig}
%\usepackage{subcaption}
%\usepackage{hyperref}
\usepackage{tikz}

@@

>>>>

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{xcolor,graphicx}
\usepackage[subfolder,cleanup]{gnuplottex}
%\usepackage{amsthm}
%\usepackage{enumitem}
%\usepackage{wrapfig}
%\usepackage{subcaption}
%\usepackage{hyperref}
\usepackage{tikz}

@@

\begin{figure*}
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
load '/home/brady/Templates/YGB.p'
#set format x '%.1f'
#set format y '%.1f'
set format z '%.1f'
set format cb '%.1f'
set grid
set yl '$T$'
set zl '$|A|$'
set cbtics 0.2
set ztics 0.2

set yr [-2.5:2.5]

set xtics ('Loss' 2, 'Disp.' 6, 'Mod.' 10, 'Gain' 14)

set xtics center offset 0,-0.5

set xyplane 0

set view 45,325,1.25
set pm3d
set pm3d interpolate 5,5

#set contour surface
unset cl
unset colorbox

sp '../../Evolution.dat' u 2:1:3 w l lw 0.3 lc 8 not
\end{gnuplot}
\caption{}
\label{fig:}
\end{figure*}
